% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

Dedication \& Acknowledgments

To those no longer with us but whose memory and principles shape my work, this is not just a book---it is a resistance node. These pages do not merely describe collapse; they reveal how collapse is engineered, normalized, and monetized. This is a systems science field manual wrapped in a narrative. I offer it to anyone ready to awaken, organize, and reclaim civic feedback before the system closes.

I sincerely thank Professors Madathil (advisor), Sayama (Graduate Studies in Complex Sciences), Wu (computational tools), Wang (Probability and Statistics), Rocha (Introduction to Complex Sciences), and Scott E. Page (whose work informed our reading material). Without their sage advice, mentorship, and scholarly guidance, I would not be writing this book today.

Special acknowledgment goes to my classmates, whose critical engagement and rigorous commentary sharpened my thinking at every stage. Their thoughtful challenges and incisive feedback ensured that each idea was tested, refined, and strengthened through dialogue. Without their insight and encouragement, the essays that evolved into these chapters would have taken a far less coherent path.

\end{document}
