% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

In the months leading up to this book's final composition, I found myself returning to a singular truth: systems don't just collapse---they are collapsed. Whether by neglect, deception, greed, or violence, the slow unraveling of a society is not a passive event. It is engineered. It is chosen. It is accelerated by those who benefit most from forgetting.

I did not begin this project as a writer. I began as an observer---of intelligence failures, of systemic betrayals, of informational decay. I've lived through conflicts where memory itself was a battleground, and I've witnessed firsthand how entire societies can be bent, then broken, by weaponized falsehoods. My background is not the subject of this book, but its shadow is there---in the rigor of systems analysis, in the urgency of pattern recognition, and in the refusal to look away.

This book is a convergence of fields: complex systems science, thermodynamic theory, psychological operations, legal decay, and information warfare. Each chapter isolates a subsystem in decline---from collapsing feedback loops to judicial permissiveness, from language entropy to algorithmic control. The data are real. The models are drawn from physical law. The implications are existential.

And yet this book is not purely academic. It is a warning. A map. And a mirror.

You will see Donald Trump throughout this text, not because he is its origin point, but because he is its embodiment. His psychological profile---marked by habitual dishonesty, narcissistic injury, and unrestrained authoritarian impulses---is not a footnote. It is a signal. A system signal. One amplified by compliant institutions, weaponized media, and compromised norms.

But this book is not about Trump alone. It is about the algorithm that made him inevitable. The collapse algorithm.

To the curious reader, the skeptical analyst, the anguished patriot---I welcome you.

We begin not with answers, but with heat, memory, and loss.

space\{2em\}
\textbackslash begin\{flushright\}
\textit{Ronald J. Botelho}\textbackslash{}
\textit{Binghamton University}\textbackslash{}
\textit{June 2025}
\textbackslash end\{flushright)

\end{document}
