Chapter 15: The Way Down

We have crossed the event horizon of constitutional reversal. The
American system is no longer inching toward autocracy---it is
functionally there. The judiciary, once imagined as a brake on tyranny,
now functions as a lubricant. Supreme Court rulings no longer reflect
neutral adjudication but strategic acquiescence.

Consider the Court's silence on President Trump's unilateral military
strikes on Iran, which bypassed congressional authorization and
triggered oil price shocks. Such actions violate the War Powers
Resolution, yet legal challenges remain unheard. The Court's refusal to
enforce the separation of powers has rendered Congress theatrically
irrelevant.

These crises do not occur in isolation. They are stacked. The
administration's move to restrict federal lawmakers' access to ICE
facilities, combined with the FTC's investigation of Media Matters (a
liberal watchdog group) for allegedly colluding with advertising groups
to defund right-wing platforms like X (formerly Twitter), illustrates a
coordinated campaign to undermine opposition, manipulate information
flows, and criminalize resistance.

The authoritarian toolkit is almost complete. Mass deportation
infrastructure (e.g., Camp Lemonnier, Alligator Alcatraz), the judicial
greenlight for torture-prone extraditions, suppression of dissent on
campus, and manipulation of judicial standing form a latticework of
repression. It is no longer hypothetical.

We are witnessing legalism without justice, trials without oversight,
executive orders without constitutional restraint. The final descent
comes when institutions become performative and enforcement becomes
weaponized. This is the way down: not in fire or fury, but in memo,
ruling, and proclamation.

Invoking Landauer once more, the compression of civic agency and the
forced erasure of institutional memory incurs not only ethical cost but
physical cost. The erasure of rights is not reversible. It costs energy,
destabilizes equilibrium, and increases systemic fragility. The
thermodynamic cost of injustice compounds across time---until collapse
is no longer a question of if, but when.

And still, the burden of resistance falls on those without robes,
gavels, or titles. It falls on us.
