% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\subsection{APA 7th Edition Bibliography for Collapse Algorithm (v2)}\label{apa-7th-edition-bibliography-for-collapse-algorithm-v2}

Benkler, Y., Faris, R., \& Roberts, H. (2018). \emph{Network propaganda: Manipulation, disinformation, and radicalization in American politics}. Oxford University Press.

Cohen, J. E. (2019). \emph{Between truth and power: The legal constructions of informational capitalism}. Oxford University Press.

Hartzog, W., \& Selinger, E. (2020). \emph{Privacy's blueprint: The battle to control the design of new technologies}. Harvard University Press.

Isaac, C. (2025, May 16). Donald Trump's culture of corruption. \emph{The New Yorker}. Retrieved from https://www.newyorker.com/news/q-and-a/donald-trumps-culture-of-corruption

Lewandowsky, S., Ecker, U. K. H., \& Cook, J. (2017). Beyond misinformation: Understanding and coping with the ``post-truth'' world. \emph{Journal of Applied Research in Memory and Cognition, 6}(4), 353--369. https://doi.org/10.1016/j.jarmac.2017.07.008

Marwick, A. E., \& Lewis, R. (2017). \emph{Media manipulation and disinformation online}. Data \& Society Research Institute.

Penney, J. W. (2017). \emph{Chilling effects: Online surveillance and Wikipedia use}. Berkeley Technology Law Journal, 31(1), 117--182. https://doi.org/10.15779/Z38G44HR0C

Schumacher, B. (2015). \emph{The science of information: From language to black holes}. Yale University Press.

Sullivan, A. (2016, May 1). America's new cult of ignorance. \emph{New York Magazine}. Retrieved from https://nymag.com

U.S. Senate Select Committee on Intelligence. (2019). \emph{Report on Russian active measures campaigns and interference in the 2016 U.S. election, Volume 2}. https://www.intelligence.senate.gov/publications/report-volume-2

Walter, B. F. (2022). \emph{How civil wars start: And how to stop them}. Crown Publishing Group.

Zuboff, S. (2019). \emph{The age of surveillance capitalism: The fight for a human future at the new frontier of power}. PublicAffairs.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Note:} This bibliography will be updated as additional citations appear in future appendices and visualizations. If you have any missing sources from earlier chapters, please provide them so they may be included.

\end{document}
